Word Sense Disambiguation: Pipelining with Supervised LSA

### 2014-05-11 paper.tex
updated sections again

	It is worth noting that other similar approaches exist in recent years that are probably more powerful (but more difficult to implement). We detail them in the next slide.

	-- Probabilistic LSA: Formulated as early as 1999, this approach is based on mixture decomposition from latent class model. 
	(this is a latent variable model for co-occurrence data)
	Model fitting is done with Expectation Maximization (EM).

	-- Non-Negative Matrix Factorization: An alternative to using SVD is NNMF, which is a matrix factoring technique introduced by Lee and Seung  (2000).  Van de Cruys (2011) makes use of this technique:
	-- minimize Kullback-Leibler divergence instead of Euclidean distance

>>>>

	It is worth noting that other similar approaches exist in recent years that are probably more powerful (but more difficult to implement). We detail them in the following sections.

	\subsubsection{Probabilistic LSA}

	-- Formulated as early as 1999, this approach is based on mixture decomposition from latent class model. 
	(this is a latent variable model for co-occurrence data)
	Model fitting is done with Expectation Maximization (EM).

	\subsubsection{Non-Negative Matrix Factorization}
	-- An alternative to using SVD is NNMF, which is a matrix factoring technique introduced by Lee and Seung  (2000).  Van de Cruys (2011) makes use of this technique:
	-- minimize Kullback-Leibler divergence instead of Euclidean distance
